Quantum Interval-Valued Probability: Measurement and Probability

### 2017-10-14 prop_iop.tex
Updates from ShareLaTeX
prop_letter.tex \section{Gleason} Clean up the part moved to Born Sec.
prop_iop.tex \subsection{Application on Convexity} Updating...

@@

\begin{lemma}Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ are all
convex for any orthonormal basis~$\Omega$, then $\bar{\mu}$ is
convex.\end{lemma}

@@

\begin{lemma}When the number of elements in $\Omega$ is less than
or equal to 3, every classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
is convex.\end{lemma}

\begin{proof}Given two events~$E_{0},E_{1}\subseteq\Omega$, we
want to verify 
\begin{equation}
\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\,.\label{eq:classical-convex}
\end{equation}
When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
is a special case of equation~(\ref{eq:classical-include}). When
$E_{0}\cup E_{1}=\Omega$, we have $E_{0}^{c}\cap E_{1}^{c}=\emptyset$,
where $E_{0}^{c}=\Omega\backslash E_{0}$ and $E_{1}^{c}=\Omega\backslash E_{1}$.
Thus, 
\begin{equation}\eqalign{ 
& \bar{\mu}^{\Omega}\left(E_{0}^{c}\cup E_{1}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{0}^{c}\cap E_{1}^{c}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}^{c}\right)+\bar{\mu}^{\Omega}\left(E_{1}^{c}\right)\\ 
\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cup E_{1}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\cap E_{1}^{c}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{0}^{c}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(E_{1}^{c}\right)\right)\\ 
\Rightarrow & \bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\,. 
}\end{equation}
When the number of elements in $\Omega\le3$, one of the following
must happen
\begin{enumerate}
\item $E_{0}\cap E_{1}=\emptyset$.
\item $E_{0}\cup E_{1}=\Omega$.
\item $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$.
\end{enumerate}
so that $\bar{\mu}^{\Omega}$ is convex. \end{proof}

@@

\begin{proof}The direct consequence of the previous lemmas. \end{proof}

>>>>

\yutsung{If the core is non-empty, could the core characterize $\bar{\mu}$
comprehensively?}

@@

\begin{lemma}\label{lemma:classical-quantum-convex}Given a quantum
IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if $\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
are all convex for any orthonormal basis~$\Omega$, then $\bar{\mu}$
is convex.\end{lemma}

@@

\begin{lemma}\label{lemma:classical-convex-condition-lemma}Given
a classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$,
the following statements are true:
\begin{enumerate}
\item If $E_{0}\subseteq E_{1}$, then $\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)$.
\item If $\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)$,
then $\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup\overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap\overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)$,
where $\overline{E_{0}}=\Omega\backslash E_{0}$ and $\overline{E_{1}}=\Omega\backslash E_{1}$.
\end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}
\item $\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)=\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)$.
\item 
\begin{equation}\eqalign{ 
 & \bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\\
\Rightarrow & \bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cap \overline{E_{1}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\right)\subseteq\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{0}}\right)\right)+\bar{\mu}^{\Omega}\left(\Omega\backslash\left(\overline{E_{1}}\right)\right)\\
\Rightarrow & 2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap \overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\right]\subseteq2-\left[\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\right]\\
\Rightarrow & \bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap \overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup \overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)\,. 
}\end{equation}
\end{enumerate}
\end{proof}

\begin{lemma}\label{lemma:classical-3-elements}When the number of
elements in $\Omega$ is less than or equal to 3, every classical
IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$ is convex.\end{lemma}

\begin{proof}Given two events~$E_{0},E_{1}\subseteq\Omega$, we
want to verify 
\begin{equation}
\bar{\mu}^{\Omega}\left(E_{0}\cup E_{1}\right)+\bar{\mu}^{\Omega}\left(E_{0}\cap E_{1}\right)\subseteq\bar{\mu}^{\Omega}\left(E_{0}\right)+\bar{\mu}^{\Omega}\left(E_{1}\right)\,.\label{eq:classical-convex}
\end{equation}
When the number of elements in $\Omega\le3$, one of the following
must happen
\begin{enumerate}
\item When $E_{0}\cap E_{1}=\emptyset$, equation~(\ref{eq:classical-convex})
is a special case of equation~(\ref{eq:classical-include}). 
\item When $E_{0}\cup E_{1}=\Omega$, we have $\overline{E_{0}}\cap\overline{E_{1}}=\emptyset$,
where $\overline{E_{0}}=\Omega\backslash E_{0}$ and $\overline{E_{1}}=\Omega\backslash E_{1}$.
By equation~(\ref{eq:classical-include}), we have $\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cup\overline{E_{1}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{0}}\cap\overline{E_{1}}\right)\subseteq\bar{\mu}^{\Omega}\left(\overline{E_{0}}\right)+\bar{\mu}^{\Omega}\left(\overline{E_{1}}\right)$.
Then, lemma~\ref{lemma:classical-convex-condition-lemma} proves
equation~(\ref{eq:classical-convex}).
\item When $E_{0}\subseteq E_{1}$ or $E_{1}\subseteq E_{0}$, equation~(\ref{eq:classical-convex})
is also followed by lemma~\ref{lemma:classical-convex-condition-lemma}.
\end{enumerate}
so that $\bar{\mu}^{\Omega}$ is convex.\end{proof}

\begin{lemma}\label{lemma:quantum-convex-condition-lemma}Given a
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, the following statements
are true:
\begin{enumerate}
\item If $P_{1}=P_{0}+P_{2}$, then $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.
\item If $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$,
then $\bar{\mu}\left(\overline{P_{0}}\vee\overline{P_{1}}\right)+\bar{\mu}\left(\overline{P_{0}}\overline{P_{1}}\right)\subseteq\bar{\mu}\left(\overline{P_{0}}\right)+\bar{\mu}\left(\overline{P_{1}}\right)$,
where $\overline{P_{0}}=\Omega\backslash P_{0}$ and $\overline{P_{1}}=\Omega\backslash P_{1}$.
\end{enumerate}
\end{lemma}

\begin{proof}The direct consequence of lemma~\ref{lemma:classical-convex-condition-lemma}
and theorem~\ref{thm:sub-event-space}.\end{proof}

@@

\begin{proof}The direct consequence of lemma~\ref{lemma:classical-quantum-convex}
and lemma~\ref{lemma:classical-3-elements}. \end{proof}
